Hemodynamic responses of the Parahippocampal Place Area to spatial cues in a movie and its audio-description

### 2020-11-11 paper/main.tex
restructure discussion of anterior vs posterior PPA

% third level
% model
The third level analysis which averaged contrast estimates over subjects was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
p=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
PPA ROI masks for individual subjects and a PPA group mask of individual PPA
overlaps were created from data provided by \citep{sengupta2016extension}.

@@

% previous studies: visual
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to face or
objects (e.g. \citep{epstein1998ppa, epstein1999parahippocampal}) whereas one
study using spoken sentences reported mixed results \citep{aziz2008modulation}.
% we use similar statistical models but with naturalistic stimuli
Here, we use statistical models that are similar to previous studies that used
small sets of experimentally controlled stimuli to investigate hemodynamic brain
responses during two naturalistic stimuli.
% more than just one contrast
We computed varying GLM contrasts that differed in the contrasted categories and
the amount of available data to test the robustness of our findings in both
stimuli.
% comparison to localizer experiment
We compare results of the primary contrast of each stimulus on the level of
individual subjects to results that we gained from a dedicated visual localizer
paradigm done with the same subjects \citep{sengupta2016extension}.
% summary of results main finding
Results of our whole-brain analyses suggest that the perception of verbal
``spatial information'' embedded in an auditory narrative contrasted with
``non-spatial information'' correlate with increased activation in the PPA of
both hemispheres.
% to do
\todo[inline]{this is just the main finding; other possible ``honourable''
mentions like robustness of results, AV stimulus, individual results?}

@@

% Previous studies used tasks
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but epstein1998
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from previous studies because the relevant stimulus
features were incidentally embedded in a continuous stream of auditory
information.
% conclusion
This embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests verbal spatial information is processed in
the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\todo[inline]{following: how to frame it (better) that AV merely serves as
conceptual control?; imo should be a small section anyway}
% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPAs from anterior to posterior and
expand into retrosplenial regions.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This can be attributed to the fact that we averaged the content of individual
frames after a cut and did not control for confounding features like depicted
faces or objects.
% confounds of lower perception
It further suggest low-level visual features were not averaged out leading to
clusters spanning the intracalcarine cortex.
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

% why we did a couple of contrasts
For both stimuli we created additional contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into posterior regions.
% results indicate robustness
Results of the additional contrasts indicate that our findings are robust across
contrasts and do not depend on the design of one specific contrasts.

% but
Nevertheless, results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA ROI.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements(, or
memory).\todo{which kind of memory}
% AO: auditory cortices
For example in the AO results, contrasts that compare (among other categories)
verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
significant clusters in (primary and secondary) auditory cortices.\todo{``poor
job of nuisance regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not do their fucking
job (it is still kinda innate in the contrast).
% possible reason
This could be attributed to a possible change of the soundscape and/or increased
volume when the narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% intro
Notably, results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).

\todo[inline]{following are quotes from references for brainstorming what might
theoretically make sense}

% connectivity
\citep{aminoff2013role} regarding \citep{baldassano2013differential}: a
neuroimaging study examining functional connectivity of differences between
anterior and posterior regions of the PHC show that anterior regions are more
functionally connected to retrosplenial complex (RSC) and parietal cortices,
whereas the posterior regions are more functionally connected to visual
processing regions.

% Baldassano (2013). Differential connectivity with Parahippocampal Place Area
\citep{baldassano2013differential} in general: anterior and posterior PPA
exhibit distinct connectivity patterns; object sensitivity in the PPA also has
an anterior-posterior gradient of sensitivity to scene and abstract object
stimuli.

% gradient
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules. Both subregions
activate selectively to scenes, and the parahippocampal region (at least in
macaques) is densely selfconnected (Suzuki, 2009), implying that these
subregions cooperate to build a complete representation of a scene.
%
Their distinct connectivity properties, however, suggests that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.

% from Baldassano discussion
\citep{baldassano2013differential} regarding posterior PPA: posterior regions
are more functionally connected to visual processing / occipital visual regions;
stronger responses to abstract objects in posterior PPA; posterior PPA is
concerned primarily with perception of low-level visual features and object
shape.

\citep{baldassano2013differential} discussion of posterior PPA: Posterior PPA
shows a stronger response to abstract objects than anterior PPA, and is more
strongly connected to all of occipital visual cortex, including LOC and TOS.
%
These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape.
%
Previous work has hinted that posterior PPA is more responsive to both simple
visual textures and objects; Arcaro et al. (2009) found that a posterior portion
of PPA responded about four times as strongly to a flickering checker-board
stimulus compared to an anterior portion, and that the response to objects was
greater than the response to scrambled images only in the posterior portion =>
posterior PPA may be more visually responsive than anterior PPA.
%
Our description of posterior PPA is in fact similar to the original proposal of
Aguirre et al. for a “lingual landmark area” (LLA), slightly posterior to PPA,
which was “specialized for the perception of visual stimuli with orienting
value” (Aguirre et al., 1998) and carried out bottom-up perceptual analysis to
recognize locations or landmarks (Cant and Goodale, 2007; Epstein et al., 1999).
%
Although the LLA is no longer identified as an independent region from PPA in
current studies, it is possible that the posterior portion of PPA corresponds to
the properties of the proposed LLA, offring an explanation for why this region
was localized more posteriorly than the full PPA.

\citep{baldassano2013differential} regarding anterior PPA: anterior regions are
more functionally connected to retrosplenial complex (RSC) and parietal
cortices; anterior PPA is more strongly connected to regions in the default mode
network (including the parieto-medial temporal pathway)
%
anterior PPA is involved in memory and global contextual processing; anterior
PPA is specifically connected to RSC, cIPL, medial PFC, and the lateral surface
of the anterior temporal lobe.
%
This portion of PPA is less visually responsive
to both scenes and objects, with notably low sensitivity to abstract object
stimuli.

\citep{baldassano2013differential} regarding DMN: the set of regions connected
more strongly to anterior PPA is strikingly similar to the Default Mode Network
(DMN) (Buckner et al., 2008; Fox et al., 2005; Raichle et al., 2001), which is
known to include the parahippocampal region.
%
The only portions of the DMN that do not show differential connectivity to
anterior PPA in our data are the rostral portion of the posterior cingulate
cortex (PCC) and the superior frontal cortex.  DMN has been implicated in a
large number of internally-focused tasks, one of its key roles involves
autobiographical memory (Buckner et al., 2008).  Models of recognition memory
have previously identified parahippocampal cortex as primarily encoding spatial
context information (Eichenbaum et al., 2007).
%
Data from Aminoff et al. (2007) has suggested that an anterior portion of PPA
may be involved in recall based on spatial context.
%
Our results are consistent with anterior PPA playing a more central role in
memory than posterior PPA, given anterior PPA's connectivity with the DMN. The
fact that anterior PPA had a lower sensitivity to our abstract object stimuli
does not necessarily im ply that this region does not use object information.
%
Previous work has shown that PPA responds to objects that have spatial
associations (Aminoff et al., 2007), are space-defining (Mullally and Maguire,
2011), and are navigationally-relevant (Janzen and Van Turennout, 2004).
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape.
%
If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation.
%
Further experiments will be required to determine what type of object-related
information is used in this region.

\subsubsection{anterior vs posterior PPA: contextual associations}

@@

% Aminoff (2013)
\citep{aminoff2013role} in general (s. also \citep{aminoff2006parahippocampal}:
processing of strong, long-term, contextual associations elicits activity within
the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
extending into the posterior cingulate cortex, and the precuneus), the medial
prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
[2,3,59–67].

% contextual associations in anterior vs. posterior
\citep{aminoff2006parahippocampal}: We propose that the general function of the
PHC can be thought of as processing of contextual associations.
%
A subregion of the posterior PHC is particularly optimized to process spatially
organized contextual associations, whereas more anterior regions of the PHC are
optimized to process contextual associations in other, non-spatial domains.
% posterior PPA for visual visual associative information
Spatial contextual associations are a dominant property of places and scenes,
and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
PPA; Epstein, 1998).
%
We do not argue that the PHC is not sensitive to spaces,
places, and spatial information, but rather that it is sensitive to spatial
stimuli because of the associative information (space-related associations) that
such stimuli evoke.

% Aminoff regarding contextual processing in the PHC and beyond
\citep{aminoff2006parahippocampal} regarding contextual associations processing
in PHC and beyond: We compared contextual processing of objects that are
strongly related to a specific place (e.g., an oven is found in a kitchen) with
contextual processing of objects that are highly associated with a context but
not a specific place (e.g., a birthday cake is found at a birthday party, but
the party can take place anywhere, at home, in a restaurant, at a park).
% method
Activity elicited by these two types of contextual objects was compared with the
activity elicited for objects that were only weakly associated with many
contexts (e.g., a lamp).
% results
Differential activity was found in the PHC and the RSC,
replicating the previous findings (Bar \& Aminoff, 2003, The
parahippocampal\dots).
% results 2
\citep{aminoff2006parahippocampal} Activity within the PHC, however, was
distributed along an anterior–posterior axis, with activity related to spatial
contexts focused in the posterior part of the PHC and activity evoked by
non-spatial contexts focused in the more anterior part of the PHC (Bar \&
Aminoff, 2003, Cortical analysis of visual context; Aminoff et al., 2007, The
parahippocampal cortex mediates spatial and nonspatial associations).

@@

\subsubsection{superior lateral occipital cortex (OPA; in both stimuli)}

@@

\todo[inline]{e.g. Bettencourt (2013). The Role of Transverse Occipital Sulcus
in Scene Perception; Dilks, Kanwisher (2013). The Occipital Place Area Is
Causally and Selectively Involved in Scene Perception?}

>>>>

% third level model
The third level analysis which averaged contrast estimates over subjects was
carried out using FLAME stage 1 with automatic outlier detection
\citep{beckmann2003general, woolrich2004multilevel, woolrich2008robust}.
% thresholding
Here again, Z (Gaussianised T/F) statistic images were thresholded using
clusters determined by Z>3.4 and a (corrected) cluster significance threshold of
p=.05 \citep{worsley2001statistical}.
% brain region identification
Brain regions associated with observed clusters were determined with the Jülich
Histological Atlas \citep{eickhoff2005toolbox, eickhoff2007assignment} and the
Harvard-Oxford Cortical Atlas \citep{desikan2006automated} provided by FSL.
% PPA masks
PPA region of interest (ROI) masks for individual subjects and a PPA group mask
of individual PPA overlaps were created from data provided by
\citep{sengupta2016extension}.

@@

% previous studies: visual
Previous studies reported bilaterally increased hemodynamic activity in the PPA
when participants were watching static pictures of landscape compared to
pictures of faces or objects (e.g. \citep{epstein1998ppa,
epstein1999parahippocampal}) whereas one study using spoken sentences reported
mixed results \citep{aziz2008modulation}.
% we use similar statistical models but with naturalistic stimuli
Here, we use statistical models that are similar to previous studies that used
small sets of experimentally controlled stimuli to investigate hemodynamic brain
responses during two naturalistic stimuli.
% more than just one contrast
We computed varying GLM contrasts that differed in the contrasted categories and
the amount of available data to test the robustness of our findings in both
stimuli.
% comparison to localizer experiment
We compare results of the primary contrast of each stimulus on the level of
individual subjects to results that we gained from a dedicated visual localizer
paradigm done with the same subjects \citep{sengupta2016extension}.
% summary of results main finding
Results of our whole-brain analyses suggest that the perception of verbal
``spatial information'' embedded in an auditory narrative contrasted with
``non-spatial information'' is correlated with increased activation in the
anterior PPA of both hemispheres.
% to do
\todo[inline]{this is just the main finding; other possible ``honourable''
mentions like robustness of results, AV stimulus, individual results?}

@@

% Previous studies used tasks
Usually studies that use small sets of experimentally controlled stimuli also
employ a task to keep subjects attentive to the stimuli.
% but epstein1998
Nevertheless, one early block-design study \citep{epstein1998ppa} compared
results from a paradigm that employed a (perceptual) judgment task of static
pictures to the same paradigm but without that task.
% results during no task
Hemodynamic activity was less but still significantly increased when
participants had no task to keep them alert and attentive to the stimuli.
% we have no task neither
Our paradigm is similar in that sense that our participants had no behavioral or
cognitive task (e.g. forming a mental image of the stimuli; cf.
\citep{ocraven2000mental})  but just had to ``enjoy the audio-description''.
% but we are still different
Our paradigm still differs from \citep{epstein1998ppa} because the relevant
stimulus features were incidentally embedded in a continuous stream of auditory
information.
% conclusion
The embeddedness prevents participants from making assumptions about the
investigated perceptual process by just being exposed to the paradigm and thus
mimics experiencing the world outside the lab more closely.
% concluding statement: kinda automatic process
The lack of a task further suggests that verbal spatial information is processed
in the PPA in an automatic fashion and does not necessarily rely on deliberately
paying attention to spatial information.

\todo[inline]{following: how to frame it (better) that AV merely serves as
conceptual control?; imo should be a small section anyway}
% AV stimulus
Group results of the AV stimulus' primary contrast yielded bilateral clusters
that span the group overlap of individual PPA ROIs from anterior to posterior.
% difference in location/size to AO and VIS
Clusters also expand into more posterior regions (occipital fusiform gyrus,
lingual gyrus, and intracalcarine cortex).\todo{which of these regions (do not
overlap) with group ROI?}
% confound of higher perception
This larger extension, especially into the primary visual cortex, can be
attributed to the fact that we averaged the content of individual frames after a
cut and did not control for confounding features like depicted faces or
objects,and low-level visual features.
% cross-modal control purpose?
\todo[inline]{concluding statement regarding AV vs AO and cross-modality of
results?}

@@

% why we did a couple of contrasts
For both stimuli we created additional contrasts that varied the amount of
events available for the analysis and how well the annotated events within
categories on average matched the stimulus type that we assumed to be
preferentially processed in the PPA.
% PPA AO
Regarding contrasts of the AO stimulus, six of eight contrasts show significant
bilateral clusters in the anterior part of the group PPA overlap.
% PPA AV
Regarding contrasts of the AV stimulus, all five contrasts show significant
bilateral clusters in the PPA but extending into more posterior brain regions.
% results indicate robustness
Thus, the results of the additional contrasts indicate that our findings are
robust across contrasts and do not depend on the design of one specific
contrasts.

% but
Nevertheless, results also suggest that localization performance depends on the
amount of available data and how well the feature space is modeled.
% example
For example, contrast 8 of the AO stimulus (\texttt{se\_new} > texttt{se\_old})
that used the most heterogeneous categories comprising the least amount of
events yielded neither a significant cluster in the right-hemispheric nor
left-hemispheric PPA.
% concluding statement
Hence, investigators using model-driven analyses have to consider how many
events a stimulus to be chosen may provide and how homogeneous the events to be
averaged might be.

% ``confounding'' clusters
Despite performing a whole brain analysis, we do not find many (random) clusters
in single contrasts or even systematically across contrasts that hamper the
interpretation of results.\todo{ouff\dots}
% AV: null results regarding attention and eye movements
For example in the AV results, we do not find significant clusters that could be
attributed to cognitive processes like attention, eye movements(, or
memory).\todo{which kind of memory}
% AO: auditory cortices
For example in the AO results, contrasts that compare (among other categories)
verbal cues about the change of a setting (\texttt{se\_new} > \texttt{se\_old})
to categories that do not cue a change of a setting (contrasts 2, 3, 6, 7) show
significant clusters in (primary and secondary) auditory cortices.\todo{``poor
job of nuisance regressors?}
% averaging vs. nuisance regressors
This suggests that variance correlating with lower level auditory processes was
not averaged out across trials and nuisance regressors did not do their fucking
job (still, it is kinda innate in the contrast).\todo{the word ''fuck`` is not
acceptable}
% possible reason
This could be attributed to a possible change of the soundscape and/or increased
volume when the narrative switches to a new setting.
% concluding statement
Thus, investigators that use model-driven methods to investigate brain functions
using naturalistic stimuli should (extensively) annotate the stimulus material
and test for correlations among variables.

@@

% intro
Notably, results of the AO contrasts consistently yielded significant clusters
spatially constrained to the anterior part of the PPA group overlap (and
anterior part of significant clusters of the AV contrasts).
% intro to connectivity and object gradient
Previous studies suggest that posterior and anterior part of the PPA show both a
difference in connectivity profiles \citep{baldassano2013differential} and a
gradient in sensitivity to scene and abstract object stimuli
\citep{arcaro2009retinotopic, aminoff2007parahippocampal,
baldassano2013differential}.
% high level summary: posterior

\paragraph{posterior: connectivity \& object sensitivity}

% Baldassano (2013): Our description of posterior PPA is in fact similar to the
% original proposal of Aguirre et al. for a “lingual landmark area” (LLA),
% slightly posterior to PPA, which was “specialized for the perception of visual
% stimuli with orienting value” (Aguirre et al., 1998) and carried out bottom-up
% perceptual analysis to recognize locations or landmarks (Cant and Goodale,
% 2007; Epstein et al., 1999). Although the LLA is no longer identified as an
% independent region from PPA in current studies, it is possible that the
% posterior portion of PPA corresponds to the properties of the proposed LLA,
% offering an explanation for why this region was localized more posteriorly
% than the full PPA.

% connectivity
The posterior PPA is more functionally connected to the occipital visual cortex,
including lateral occipital cortex (LOC) and transverse occipital sulcus (TOS)
\citep{baldassano2013differential}.
% LOC and TOS
[These regions have well-defined retinotopic maps (Arcaro et al., 2009; Nasr et
al., 2011), and are associated with the perception of low-level visual features
and object shape \citep{baldassano2013differential}.]
% object sensitivity
Previous work has hinted that posterior PPA is more responsive to both simple
visual textures and (abstract) objects \citep{arcaro2009retinotopic,
baldassano2013differential}.
%
The posterior portion of PPA responded about four times as strongly to a
flickering checker-board stimulus compared to an anterior portion, and that the
response to objects was greater than the response to scrambled images only in
the posterior portion => posterior PPA may be more visually responsive than
anterior PPA \citep{arcaro2009retinotopic}.
% in summary: posterior
In summary, the posterior PPA is more concerned with perception of low-level
visual features and object shape.

\paragraph{anterior: connectivity \& (non) contextual sensitivity}

The anterior PPA is more functionally connected to the RSC and parietal cortices
(caudal inferior parietal lobe; cIPL)[, medial PFC, and the lateral surface of
the anterior temporal lobe] \citep{baldassano2013differential}.
% default mode network
[anterior PPA is also more strongly connected to regions in the default mode
network (including the parieto-medial temporal pathway).
\citep{baldassano2013differential}.]
% DMN details
The set of regions connected more strongly to anterior PPA is strikingly similar
to the Default Mode Network (DMN) (Buckner et al., 2008; Fox et al., 2005;
Raichle et al., 2001), which is known to include the parahippocampal region (the
only portions of the DMN that do not show differential connectivity to anterior
PPA in our data are the rostral portion of the posterior cingulate cortex (PCC)
and the superior frontal cortex) \citep{baldassano2013differential}.
% DMN and contextual association
DMN has been implicated in a large number of internally-focused tasks, one of
its key roles involves autobiographical memory (Buckner et al., 2008).  Models
of recognition memory have previously identified parahippocampal cortex as
primarily encoding spatial context information (Eichenbaum et al., 2007)
\citep{baldassano2013differential}.
% Baldassano regarding Aminoff
Data from \citep{aminoff2007parahippocampal} has suggested that an anterior
portion of PPA may be involved in recall based on spatial context
\citep{baldassano2013differential}.
%
Given anterior PPA's connectivity with the DMN.Our results are consistent with
anterior PPA playing a more central role in memory than posterior PPA
\citep{baldassano2013differential}.

% object sensitivity
The anterior PPA is less visually responsive to both scenes and objects, with
notably low sensitivity to abstract object stimuli, and more involved in memory
and global contextual processing \todo{quotes???}
%
The fact that anterior PPA had a lower sensitivity to our abstract object
stimuli does not necessarily imply that this region does not use object
information \citep{baldassano2013differential}.
%
Previous work has shown that PPA responds to objects that have spatial
associations (Aminoff et al., 2007), are space-defining (Mullally and Maguire,
2011), and are navigationally-relevant (Janzen and Van Turennout, 2004).

\paragraph{conclusion: subregions}

\todo[inline]{re-read Baldassano (2013)}

@@

% Aminoff
\citep{aminoff2013role} in general (s. also \citep{aminoff2007parahippocampal}:
processing of strong, long-term, contextual associations elicits activity within
the PHC, as well as the RSC (which includes regions of the retrosplenial cortex,
extending into the posterior cingulate cortex, and the precuneus), the medial
prefrontal cortex (MPFC), and the transverse occipital sulcus (TOS) (Figure 2)
[2,3,59–67].
% Aminoff: contextual associations in anterior vs. posterior
\citep{aminoff2007parahippocampal} propose that a subregion of the posterior PHC
is particularly optimized to process spatially organized contextual
associations, whereas more anterior regions of the PHC are optimized to process
contextual associations in other, non-spatial domains.
% posterior PPA for visual visual associative information
Spatial contextual associations are a dominant property of places and scenes,
and thus scenes consistently activate this posterior subregion of the PHC (e.g.,
PPA; Epstein, 1998).
%
We do not argue that the PHC is not sensitive to spaces, places, and spatial
information, but rather that it is sensitive to spatial stimuli because of the
associative information (space-related associations) that such stimuli evoke.

% Aminoff regarding contextual processing in the PHC and beyond
\citep{aminoff2007parahippocampal}: We compared contextual processing of objects
that are strongly related to a specific place (e.g., an oven is found in a
kitchen) with contextual processing of objects that are highly associated with a
context but not a specific place (e.g., a birthday cake is found at a birthday
party, but the party can take place anywhere, at home, in a restaurant, at a
park).
% method
Activity elicited by these two types of contextual objects was compared with the
activity elicited for objects that were only weakly associated with many
contexts (e.g., a lamp).
% results
Differential activity was found in the PHC and the RSC, replicating the previous
findings (Bar \& Aminoff, 2003, The parahippocampal\dots).
% results 2
\citep{aminoff2007parahippocampal} Activity within the PHC, however, was
distributed along an anterior–posterior axis, with activity related to spatial
contexts focused in the posterior part of the PHC and activity evoked by
non-spatial contexts focused in the more anterior part of the PHC (Bar \&
Aminoff, 2003, Cortical analysis of visual context; Aminoff et al., 2007, The
parahippocampal cortex mediates spatial and nonspatial associations).

% Baldassano (2013): PPA subregions
Data suggest that PPA might contain identifiable subregions, but subregions
should not be considered as completely independent modules. Both subregions
activate selectively to scenes, implying that these subregions cooperate to
build a complete representation of a scene [that sentence is taken from
\citep{baldassano2013differential}].
% Baldassano (2013): conclusion
Their distinct connectivity properties, however, suggests that each may be
involved in specific aspects of visual and cognitive processing involved in the
overarching goal of scene understanding.
%
These types of responses require spatial memory and cannot be based purely on
visual features like object shape.
%
If anterior PPA is involved in processing spatial context, then space-defining
or navigationally-relevant objects could activate anterior PPA more strongly
than our abstract objects, which were unfamiliar and provided no sense of
context or orientation.
%
Further experiments will be required to determine what type of object-related
information is used in this region.

@@

\subsubsection{superior lateral occipital cortex (TOC / OPA?)}

@@

\todo[inline]{numbers of contrast in AO \& AV that show sign. clusters in
LOC}

\todo[inline]{e.g. Bettencourt (2013). The Role of Transverse Occipital Sulcus
    in Scene Perception; Dilks, Kanwisher (2013). The Occipital Place Area Is
    Causally and Selectively Involved in Scene Perception; Grill-Spector (2003).
    The neural basis of object perception; Nakamura (2000). Functional
    delineation of the human occipito-temporal areas; Nasr (2011).
    Scene-selective cortical regions in human and nonhuman primates; Hasson
    (2003). Large-scale mirror-symmetry organization; MacEvoy and Epstein
    (2007). Position selectivity in scene- and object-responsive\dots; Dilks
(2011). Mirror-image sensitivity and invariance in object \& scene processing}
